AIR4Children: Artificial Intelligence and Robotics for Children

### 2021-02-14 article/tex/submission.tex
poslishes section 2

\section{Open Source Software and Hardware for AI and Robotics}
In 1978 Donald Knuth designed \TeX, typesetting system, which is a role model for open source projects where organisational phases of its development and the relative simple accessibility to users were crucial to its success \cite{gaudeul2007}.
Then, in 1983 Richard Stallman, with the frustration to not freely inspect, modify or share software, founded the GNU project to then create a GNU manifesto stating the freedom to run, study, copy, and make modification of software \cite{stallman1985}.
That said, such projects were the corner stone of what is known as the Open Software Initiative, founded by Bruce Perens and Eric S. Raymond in 1998, stating that projects must be free redistributable, code must be available and distributable, modification must be allowed and many others \cite{brasseur2018}.
Following a similar spirit that software can be used, studied, copied, modified, and redistributed without restriction, projects of open source hardware started to emerge in mid 2000s emerged (e.g., OpenCores, RepRap (3D printing), Arduino, Adafruit and SparkFun) \cite{pearce2013}.

In the last decade, another wave of scientific innovation has been emerging in the field of AI due to open source software frameworks (e.g. pytorch, tensorflow, etc.) and places to distribute these (e.g. GitHub, gitlab, bitbucket) \cite{matelabs2017}
However, little has been seen accross the fields of AI and Robotics. 
For instance, OTTO DIY is an educational open source robot founded in 2016 by Camilo Parra, the community of OTTO has more than 20,000 users from 20 countries and more than 100 re-designs of the robot \cite{OttoDIY:2016}.
With regards to Robotics, the JPL Open Source Rover, created by engineers at NASA and initially released in April 2018, is a good reference as it is designed with detailed instructions for constructions for high school students and beyond, and technical specifications, 3D models, assembly instructions are fully available \cite{OSR:2018}.
Recently, engineers at NVIDIA in 2019, released nano JetBot as a affordable, education and fun platform  "to give the hands on experience needed to create entirely new AI projects" \cite{nanoJetBot:2019}. 
That said, there is room to create platforms to create educational resources to teach AI and robotics, as pointed by JetBot, in a more affordable, educational and fun characteristics.
Table~\ref{tab:opensourceprojects} summarises three open source projects with year of establishment and cost.

@@

%BLURS
%which will be helpful to teach many didactic activities where children 
%can interact with the robot and learn concepts of robotics, linear algebra, 
%machine learning, and deep learning.

>>>>

\section{Open Source Software and Hardware for AI and Robotics}
In 1978 Donald Knuth designed \TeX, typesetting system, which is a role model for open source projects where organisational phases of its development and the relative and simple accessibility to users were crucial to its success \cite{gaudeul2007}.
Then, in 1983 Richard Stallman, with the frustration to not freely inspect, modify or share software, founded the GNU project to then create a GNU manifesto \cite{stallman1985}.
Such projects were the corner stone of what is known as the Open Software Initiative, founded by Bruce Perens and Eric S. Raymond in 1998, stating that projects must be free redistributable, code must be available and distributable, modification must be allowed, etc \cite{brasseur2018}.
Following a similar spirit that software can be used, studied, copied, modified, and redistributed without restriction, projects of open source hardware started to emerge in mid 2000s emerged (e.g., OpenCores, RepRap (3D printing), Arduino, Adafruit and SparkFun) \cite{pearce2013}.

Then, in the last decade, another wave of scientific innovation has been emerging in the field of AI due to open source software frameworks (e.g. pytorch, tensorflow, etc.) and places to distribute these (e.g. GitHub, gitlab, bitbucket) \cite{matelabs2017}.
However, little has been done for child-centred AI and Robotics. 
For instance, Otto DIY is an educational open source robot founded in 2016 by Camilo Parra, where the community of OTTO has more than 20,000 users from 20 countries and more than 100 re-designs of the robot \cite{OttoDIY:2016}.
Another example is the JPL Open Source Rover, created by engineers at NASA and initially released in April 2018, which it is designed with detailed instructions for constructions for mainly high school students, and open source technical specifications, 3D models and assembly instructions \cite{OSR:2018}.
Recently, engineers at NVIDIA in 2019, released nano JetBot as a affordable, education and fun platform  "to give the hands on experience needed to create entirely new AI projects" \cite{nanoJetBot:2019}.

That said, there is opportunity to create educational resources to teach AI and robotics to children aiming to be, as pointed by JetBot, affordable, educational and fun \cite{nanoJetBot:2019}, where our prototype is starting to tackle few of them. 
Table~\ref{tab:opensourceprojects} summarises open source projects with year of establishment and cost.

%BLURS

@@

%which will be helpful to teach many didactic activities where children 
%can interact with the robot and learn concepts of robotics, linear algebra, 
%machine learning, and deep learning.
